Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-10-25 Ch1_movement_rates/Ch1_Figures.Rmd
not loading those other scenarios

# Dispersion and Dispersal --------------------------------------------------------------------

cp.summ.df %>%
  dplyr::select(av.disp, dsprsn, model) %>% 
  bind_rows(., pp.summ.df %>%
              dplyr::select(av.disp, dsprsn, model)) %>%
  bind_rows(., np.summ.df %>%
              dplyr::select(av.disp, dsprsn,  model) %>%
              mutate(model = "np")) %>% 
  # bind_rows(., ppi.summ.df %>% 
  #             dplyr::select(av.disp, dsprsn, model) %>% 
  #             mutate(model = "ppi")) %>% 
  mutate(model = factor(model, levels = c("cp", "pp",
                                          #"ppi",
                                          #"np_1", "np_2", "np_3",
                                          "np"))) -> disp_df
```

@@

@@

joint_weib %>% 
  mutate(model = factor(model, levels = c("cp", "pp",
                                          # "ppi", "np_1", "np_2", "np_3"
                                          "np"))) -> joint_weib
```

@@

>>>>

# Real data --------------------------------------
load("Ch1_movement_rates/sims_backup/datagen_cpr.RData")
load("Ch1_movement_rates/sims_backup/datagen_ppr.RData")
load("Ch1_movement_rates/sims_backup/datagen_npr.RData")

load("Ch1_movement_rates/sims_backup/weib_cpr.RData")
load("Ch1_movement_rates/sims_backup/weib_ppr.RData")
load("Ch1_movement_rates/sims_backup/weib_npr.RData")

```{r}
# Dispersion and Dispersal --------------------------------------------------------------------

cp.summ.df %>%
  dplyr::select(av.disp, dsprsn, model) %>% 
  bind_rows(., pp.summ.df %>%
              dplyr::select(av.disp, dsprsn, model)) %>%
  bind_rows(., np.summ.df %>%
              dplyr::select(av.disp, dsprsn,  model) %>%
              mutate(model = "np")) %>% 
  # bind_rows(., ppi.summ.df %>% 
  #             dplyr::select(av.disp, dsprsn, model) %>% 
  #             mutate(model = "ppi")) %>% 
  mutate(model = factor(model, levels = c("cp", "pp",
                                          #"ppi",
                                          #"np_1", "np_2", "np_3",
                                          "np"))) -> disp_df

cpr.summ.df %>%
  dplyr::select(av.disp, dsprsn, model) %>% 
  bind_rows(., ppr.summ.df %>%
              dplyr::select(av.disp, dsprsn, model)) %>%
  bind_rows(., npr.summ.df %>%
              dplyr::select(av.disp, dsprsn,  model) %>%
              mutate(model = "npr")) %>% 
  mutate(model = factor(model, levels = c("cpr", "ppr",
                                          "npr"))) -> disp_r_df
```

@@

### With the real data

```{r}
disp_r_df %>%
  group_by(., model) %>%
  sample_n(., 1000) %>%
  ggplot(., aes(y = dsprsn, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Dispersion", y = "Dispersion in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> pr_dispersion

disp_r_df %>%
  group_by(., model) %>%
  sample_n(., 1000) %>%
  ggplot(., aes(y = av.disp, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Average dispersal", y = "Dispersal in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> pr_dispersal

plot_grid(pr_dispersal, pr_dispersion)
```

@@

joint_weib %>% 
  mutate(model = factor(model, levels = c("cp", "pp",
                                          # "ppi", "np_1", "np_2", "np_3"
                                          "np"))) -> joint_weib

weib.boot.cpr %>%
  dplyr::select(., est.shape, est.scale, boot, model) %>%
  bind_rows(., weib.boot.ppr %>%
              dplyr::select(., est.shape, est.scale, boot, model)) %>%
  bind_rows(., weib.boot.npr %>%
              mutate(model = "npr") %>%
              dplyr::select(., est.shape, est.scale, boot, model)) -> joint_r_weib

joint_r_weib %>% 
  mutate(model = factor(model, levels = c("cpr", "ppr",
                                          # "ppi", "np_1", "np_2", "np_3"
                                          "npr"))) -> joint_r_weib
```

@@

Real data

```{r}
joint_r_weib %>%
  group_by(model) %>%
  sample_n(., 100) %>%
  ggplot(., aes(x = model, y = est.shape)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(position = position_jitter(0.1)) +
  geom_hline(aes(yintercept = 1), lty = "dashed") +
  labs(title = "Shape") +
  #scale_y_continuous(limits = c(0, 2)) +
  theme_bw() -> weib_r_shape

joint_r_weib %>%
  group_by(model) %>%
  sample_n(., 100) %>%
  ggplot(., aes(x = model, y = est.scale)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(position = position_jitter(0.1)) +
  labs(title = "Scale") +
  theme_bw() -> weib_r_scale

plot_grid(weib_r_shape, weib_r_scale)

# ggsave2(filename = "Ch1_movement_rates/Figures/weib_plot.png")
```
